Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-06 tex/paper1/paper1.tex
paper edits

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as the
superior description of the observed Fourier power spectrum.  This
model is consistent with previous observations by TRACE of power in
the frequency range of 1 - 10 mHz.  The moss region shows the largest
presence of this excess emission.

It would be tempting to take this excess contribution and infer a
distribution of field line angles with the solar surface.  This
distribution relies on the assumption that all the
Gaussian-distributed component is entirely due to the channeling of
photospheric oscillatory power up to ``coronal'' heights and
temperatures.

The AIA 171\AA\ and 193\AA\ wavebands are relatively wide, and include
contributions from plasma at many different temperatures, heights in
the atmosphere, and many different elements \cite{}.  A deeper
understanding of the contributions from these different plasmas is
required before a good estimate of the distribution of the angle
coronal loop footpoints make with the surface can be made.

Finally, only two models of the Fourier power spectrum are considered.
The choice of equation \ref{eqn:pwrlawbump} is motivated by previous
observations.  However, other models are certainly possible.  For
example, \cite{1993ASPC...42..111H} modelled the

@@

Each energy deposition event is modeled as an exponentially decaying
function of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{T}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
energy $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the energy in each event depends on its time scale $T$ such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown \cite{} that the observed power spectrum can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}

@@

Comparing the \Fps\ of the simulated observations to the \Fps\ of the
data will bring new constraints on the simulations that will hopefully
improve our understanding of the temporal behavior of the solar corona.

@@

\bibliography{references}
\end{document}

>>>>

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
the superior description of the observed Fourier power spectrum. The
moss region shows the greatest contribution from the Gaussian
distribution $G(\nu)$ over the background power law.

\cite{2005ApJ...624L..61D} show that it is possible to leak
oscillatory power from lower in the atmosphere to the upper reaches of
the atmosphere through the simple expedient of tilting the field line.
This changes the acoustic cutoff frequency and so allows wave energy
to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
represents conditions in the solar atmosphere, then it should be
possible to infer a distribution of field line angles with the solar
surface using \cite{2005ApJ...624L..61D} and the observed power
distribution $G(\nu)$.  This would constrain the distribution of field
line angles in the lower atmosphere in different regions of the solar
surface.

@@

Each energy deposition event is modeled as an exponentially decaying
function of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{T}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
energy $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the energy in each event depends on its time scale $T$ such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed power spectrum can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}

@@

Time series of AIA 171\AA\ and 193\AA images show approximately power
law like properties over all regions of the solar surface.  The power
spectra have been modelled using a power-law power spectrum with a
constant background summed with a localized contribution

Comparing the \Fps\ of the simulated observations to the \Fps\ of the
data will bring new constraints on the simulations that will hopefully
improve our understanding of the temporal behavior of the solar
corona.  Further, this paper only considers two of the AIA wave-bands
that are sensitive to higher temperatures.  Using the other
wave-bands, in comparison with the

Finally, only two models of the Fourier power spectrum have been
considered.  The choice of equation \ref{eqn:pwrlaw} is motivated by
the observations of all four regions considered.  Equation
\ref{eqn:pwrlawbump} was motivated by previous observations of
oscillatory content in the solar atmosphere.  Equation
\ref{eqn:pwrlawbump} is shown to be the preferred model in all cases.

@@

\bibliography{references}
\end{document}
However, other more complex models are certainly possible.  For
example, \cite{1993ASPC...42..111H} modelled the background
chromospheric Fourier power spectrum of a series of Ca-II K-line
images using a 19-parameter fit consisting of a constant background,
three components of the form
\begin{equation}
\label{eqn:harvey1}
P(\nu) \propto \frac{1}{1 + (2\pi \nu T_{0})^{b}}.
\end{equation}
and two components of the form
\begin{equation}
\label{eqn:harvey2}
P(\nu) \propto
\left(
\frac{\nu}{\nu_{0}}
\right)^{c}
\left(
\frac{\Gamma^{2}}{(\nu-\nu_{0})^{2} + \Gamma^{2}}
\right)^{b}.
\end{equation}
